Statistical analysis of proteomics experiments with R and MSstats (v3.0.9)

### 2015-09-18 MSstats_manual_RMarkdown.Rmd
Meena : 2015.sep 13, minor updates

```{r, eval=T}
# default option
DDA2009.TMP.random <- dataProcess(raw = DDA2009.superhirn,  fillIncompleteRows = TRUE,
                           normalization = 'equalizeMedians',
                           summaryMethod = 'TMP',
                           censoredInt=NULL)
```

@@

Besides summarizing observations with linear models MSstats also offers a summarization option using linear model, and as sum of log-intensities, which is the default Skyline behaviour. `summaryMethod="linear"` with `censoredInt=NULL` assumes that all NAs are randomly missing and use `lm` or `lmer` for parameter estimation. `summaryMethod="linear"` with `censoredInt="NA"` assumes that NA intensities are censored, not detected because intensities are below the cutoff. Then use AFT model with left-censored for parameter estimation. 'cutoffCensored' is the same as `summaryMethod="TMP"`. For `summaryMethod="linear"`, AFT model is only used for parameter estimation, not for imputation. Therefore `MBimpute=TRUE` with `summaryMethod="linear"` doesn't work (no imputation before parameter estimation, the same with `MBimpute=FALSE`).

@@

### 2. different option for dataProcess
Only different options in `dataProcess` you should use for Skyline output are `skylineReport=TRUE` (remove `Truncated=TRUE` rows and handle intensity=0) and `censoredInt="0"`(use intensity=0 as censored to handle missing values).

@@

If you have MaxQuant output, please follow this section. Here controlled mixture data with dynamic range bench mark (Cox, 2014 in MCP) is used to demonstrate.

>>>>

```{r, eval=T}
# no action for missing values.
DDA2009.TMP.random <- dataProcess(raw = DDA2009.superhirn,  fillIncompleteRows = TRUE,
                           normalization = 'equalizeMedians',
                           summaryMethod = 'TMP',
                           censoredInt=NULL)
```

@@

Besides summarizing observations with linear models MSstats also offers a summarization option using linear model, and as sum of log-intensities, which is the default Skyline behaviour. `summaryMethod="linear"` with `censoredInt=NULL` assumes that all NAs are randomly missing and use `lm` or `lmer` for parameter estimation. `summaryMethod="linear"` with `censoredInt="NA"` assumes that NA intensities are censored, not detected because intensities are below the cutoff. Then use AFT model with left-censored for parameter estimation. (`Surv` function with left-censored and gaussian distribution from `Survival` package.) cutoffCensored' is the same as `summaryMethod="TMP"`. For `summaryMethod="linear"`, AFT model is only used for parameter estimation, not for imputation. Therefore `MBimpute=TRUE` with `summaryMethod="linear"` doesn't work (no imputation before parameter estimation, the same with `MBimpute=FALSE`).

@@

### 2. Options for Skyline in dataProcess
The options in `dataProcess` you should be careful for Skyline output are `skylineReport=TRUE` (remove `Truncated=TRUE` rows and handle intensity=0) and `censoredInt="0"`(use intensity=0 as censored to handle missing values and in this case, NA values are assumed as random missing).

@@

If you have MaxQuant output, please follow this section. Here controlled mixture data with dynamic range bench mark (Cox, 2014 in MCP) is used to demonstrate. This dataset is available in [MSstats material github](https://github.com/MeenaChoi/MSstats_material) in the folder named 'example dataset/DDA_controlledMixture20014'.
